Meta-analysis of the Interoceptive Accuracy Scale

### 2025-10-31 analysis/study2.qmd
updated study2

data <- rbind(
  data,
  pool_coef(with = "PHQ15_Sum", component="Depression", category = "Mood", name = "Somatic Concerns - PHQ-15",unequalrange=TRUE), 
  pool_coef(with = "PHQ9_Sum", component="Depression", category = "Mood", name = "Depression - PHQ-9", unequalrange=TRUE), 
  pool_coef(with = "BDI_Sum", component="Depression", category = "Mood", name = "Depression - BDI"), 
  pool_coef(with = "PHQ4_Depression", component="Depression", category = "Mood", name = "Depression - PHQ-4"),
  pool_coef(with = "DEP", component = "Depression", category = "Mood", name = "Depression - MFQ")
)
```

@@

data <- rbind(
  data,
  pool_coef(with = "STAIT_Mean", component="Anxiety", category = "Mood", name = "Anxiety - STAI-T", unequalrange=TRUE), 
  pool_coef(with = "PHQ4_Anxiety", component="Anxiety", category = "Mood", name = "Anxiety - PHQ-4"),
  pool_coef(with = "GAD7_Sum", component="Anxiety", category = "Mood", name = "Anxiety - GAD-7")
)
```

>>>>

data <- rbind(
  data,
  pool_coef(with = "PHQ15_Sum", component="Depression", category = "Mood", name = "Somatic Concerns - PHQ-15",unequalrange=TRUE), 
  pool_coef(with = "PHQ9_Sum", component="Depression", category = "Mood", name = "Depression - PHQ-9", unequalrange=TRUE), 
  pool_coef(with = "BDI_Sum", component="Depression", category = "Mood", name = "Depression - BDI"), 
  pool_coef(with = "PHQ4_Depression", component="Depression", category = "Mood", name = "Depression - PHQ-4", unequalrange=TRUE),
  pool_coef(with = "DEP", component = "Depression", category = "Mood", name = "Depression - MFQ")
)
```

@@

data <- rbind(
  data,
  pool_coef(with = "STAIT_Mean", component="Anxiety", category = "Mood", name = "Anxiety - STAI-T", unequalrange=TRUE), 
  pool_coef(with = "PHQ4_Anxiety", component="Anxiety", category = "Mood", name = "Anxiety - PHQ-4",  unequalrange=TRUE),
  pool_coef(with = "GAD7_Sum", component="Anxiety", category = "Mood", name = "Anxiety - GAD-7")
)
```
